---
title: "GOT_16s_Analysis"
output: html_document
date: "2024-05-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,warning=FALSE,message=FALSE}
# Imports
library(dada2)
library(ape)
library(vegan)
library(phyloseq)
library(ggplot2)
library(vegan)
library(plyr)
library(dplyr)
library(ape)
library(plotly)
```

```{r}
path <- "/home/nickel.h/GOT_Analysis/16s/16s Read Files"
list.files(path)  
```

```{r}
# Assign which files are forward/reverse in that path
fnFs <- sort(list.files(path, pattern="-R1.fastq",full.names=TRUE))
fnRs <- sort(list.files(path, pattern = "-R2.fastq", full.names = TRUE))

# Name the samples 
sample.names <- sapply(strsplit(basename(fnFs), "-"), function(x) x[[1]])
sample.names
```

```{r}

# Check quality
plotQualityProfile(fnFs[5:10])  # Early copper samples
plotQualityProfile(fnRs[25:30]) 

```

```{r}

# Copy filtered samples to subdirectory
filt_path <- file.path(path, "filtered_GOT_16s")
filtFs <- file.path(filt_path, paste0(sample.names, "_F_filt.fastq.gz"))
filtRs <- file.path(filt_path, paste0(sample.names, "_R_filt.fastq.gz"))

# Filter / Trim

out <- filterAndTrim(fnFs, filtFs, fnRs, filtRs, truncLen=c(150,150),
                     maxN=0, maxEE=c(2,5), truncQ=2, rm.phix=TRUE,trimLeft = 12,
                     compress=TRUE, multithread=TRUE, matchIDs=TRUE)

saveRDS(out,"out_16s.rds")
out <- readRDS("out_16s.rds")
head(out)

```

```{r}

# Get existing files that weren't filtered out
exists <- file.exists(filtFs)

# Learn error rate
errF <- learnErrors(filtFs[exists], multithread=TRUE) #100193520 total bases in 596390 reads from 52 samples will be used for learning the error rates.
saveRDS(errF, "errF_GOT_16s.rds")
errR <- learnErrors(filtRs[exists], multithread=TRUE) #100193520 total bases in 596390 reads from 52 samples will be used for learning the error rates.
saveRDS(errR, "errR_GOT_16s.rds")

# Reload and plot learned errors
errF <- readRDS("errF_GOT_16s.rds")
errR <- readRDS("errR_GOT_16s.rds")
plotErrors(errR, nominalQ=TRUE)
plotErrors(errF, nominalQ=TRUE)

# Derep and save with sample names
derepFs <- derepFastq(filtFs[exists], verbose=TRUE)
derepRs <- derepFastq(filtRs[exists], verbose=TRUE)
names(derepFs) <- sample.names[exists]
names(derepRs) <- sample.names[exists]

```

```{r}
# Dada step!
dadaFs <- dada(derepFs, err=errF, multithread=TRUE)
saveRDS(dadaFs, "dadaFs_16s.rds")
dadaRs <- dada(derepRs, err=errR, multithread=TRUE)
saveRDS(dadaRs, "dadaRs_16s.rds")

# Merge paired reads
mergers <- mergePairs(dadaFs, derepFs, dadaRs, derepRs, verbose=TRUE)
saveRDS(mergers, "merger_GOT_16s.rds")
mergers <- readRDS("merger_GOT_16s.rds")

# Construct sequence table
seqtab <- makeSequenceTable(mergers)
dim(seqtab)    # 68   4991

```

```{r}

# Remove chimeras
seqtab.nochim <- removeBimeraDenovo(seqtab, method="consensus", multithread=TRUE, verbose=TRUE)
dim(seqtab.nochim) # 68 4863
table(nchar(getSequences(seqtab.nochim)))
sum(seqtab.nochim)/sum(seqtab)  #0.9883494
saveRDS(seqtab.nochim,"seqtab_nochimeras_16s.rds")
seqtab.nochim = readRDS("seqtab_nochimeras_16s.rds")
# Create OTU table
otu_table <- data.frame(sequence =  colnames(seqtab.nochim), abundance = colSums(seqtab.nochim))

```

```{r}

#  Assign taxonomy! (using SILVA)
taxa <- assignTaxonomy(seqtab.nochim, "/home/nickel.h/GOT_Analysis/16s/silva_nr_v132_train_set.fa.gz", multithread=TRUE)
saveRDS(taxa, "taxa_16s.rds")

# Add species level
#taxa.plus <- addSpecies(taxa, "~/Desktop/GOT/Database/silva_species_assignment_v132.fa.gz", verbose=TRUE)
#saveRDS(taxa.plus, "~/Desktop/GOT/taxa_plus.rds")

```

```{r}
# Prepare data for phyloseq object
meta = read.csv("/home/nickel.h/GOT_Analysis/18s/GOT_16S_map.csv", row.names = "SampleID")
#dates <- as.Date(sample_names, format = "%Y_%m_%d")  # Adjust the format if needed
tax = readRDS("/home/nickel.h/GOT_Analysis/18s/taxa_16s.rds")
seqtab.nochim = readRDS("/home/nickel.h/GOT_Analysis/18s/seqtab_nochimeras_16s.rds")


physeq <- phyloseq(otu_table(seqtab.nochim, taxa_are_rows=FALSE), 
                   sample_data(meta), tax_table(tax))
saveRDS(physeq, 'physeq_16s.rds')

physeq
```



```{r}

# Remove samples with low reads (can't make this work)
pruned = prune_samples(sample_sums(physeq)>=20, physeq)

# Filter out really low abundance taxa

#physeq = filter_taxa(pruned, function(x) sum(x > 1) > (0.01*length(x)), TRUE)

physeq %>%
  subset_taxa(Kingdom == "Bacteria" & 
                Family != "Mitochondria" & 
                Class != "Chloroplast") -> physeq2

# Remove samples with low reads (can't make this work)
pruned = prune_samples(sample_sums(physeq)>=20, physeq2)

# Filter out really low abundance taxa
physeq2 = filter_taxa(pruned, function(x) sum(x > 1) > (0.01*length(x)), TRUE)
physeq2

library("decontam")
library(Biostrings); packageVersion("Biostrings")
dna <- Biostrings::DNAStringSet(taxa_names(physeq2))
names(dna) <- taxa_names(physeq2)
physeq2 <- merge_phyloseq(physeq2)
taxa_names(physeq2) <- paste0("ASV", seq(ntaxa(physeq2)))

sample_data(physeq2)$is.neg <- sample_data(physeq2)$Project == "Blank"
contamdf.prev <- isContaminant(physeq2, method="prevalence", neg="is.neg")
table(contamdf.prev$contaminant)
head(which(contamdf.prev$contaminant))

ps <- prune_taxa(!contamdf.prev$contaminant, physeq2)
saveRDS(ps, "ps_16s_decontam.rds")

```

```{r}
ps <- readRDS("ps_16s_decontam.rds")
physeq_GOT = subset_samples(ps, Project != "Blank")


```



```{r}
# Load necessary library
library(phyloseq)

# Calculate alpha diversity for each sample
alpha_diversity_df <- estimate_richness(physeq, measures = c("Chao1", "ACE", "Shannon", "Simpson", "Observed"))

# Convert the alpha diversity data to a data frame and add sample names as a column
alpha_diversity_df <- cbind(Sample = rownames(alpha_diversity_df), alpha_diversity_df)
rownames(alpha_diversity_df) <- NULL  # Remove row names

# View the result
head(alpha_diversity_df)

```

```{r}
# Load necessary libraries
library(phyloseq)
library(ggplot2)
library(stringr)


# Calculate Shannon diversity for each sample
shannon_diversity <- estimate_richness(physeq_GOT, measures = "Shannon")

# Extract sample names and Shannon values
shannon_diversity_df <- data.frame(Sample = rownames(shannon_diversity), Shannon = shannon_diversity$Shannon)

# Add a column from the sample metadata (e.g., Time or Treatment) for the x-axis
sample_metadata_df <- data.frame(Sample = rownames(sample_data(physeq_GOT)), Project = sample_data(physeq_GOT)$Project)  # Replace 'Time' with your column name

# Merge Shannon diversity data with the metadata
shannon_diversity_df <- merge(shannon_diversity_df, sample_metadata_df, by = "Sample")
#shannon_diversity_df$Day <- as.numeric(shannon_diversity_df$Day)

shannon_diversity_df <- shannon_diversity_df %>%
  mutate(Project = str_replace_all(Project, "TimeSeries", "Hyposalinity")) %>%
  mutate(Project = str_replace_all(Project, "Copper_tx", "Copper"))
alpha <- ggplot(shannon_diversity_df, aes(x = factor(Project), y = Shannon, fill = factor(Project))) +
  geom_boxplot() +
  labs(x = "Treatment", y = "Alpha Diversity") +
  scale_fill_manual(values = c("brown", "navyblue")) +  # Set two colors manually
  theme_minimal() +
  theme(
    legend.position = "none",  # Remove the legend
    panel.border = element_rect(color = "black", fill = NA, size = 1),  # Add a black border
    panel.background = element_rect(fill = "white")  # Ensure panel background is visible
  )+
  ylim(0, 5)  # Set y-axis range from 0 to 5



ggsave("alpha_16s.png", plot = alpha, width = 4.5, height = 4, dpi = 300)
```

```{r}
# Split data by Project
group_A <- shannon_diversity_df$Shannon[shannon_diversity_df$Project == "Copper"]
group_B <- shannon_diversity_df$Shannon[shannon_diversity_df$Project == "Hyposalinity"]

# Shapiro-Wilk test for normality
shapiro.test(group_A)
shapiro.test(group_B)

library(car)
leveneTest(Shannon ~ Project, data = shannon_diversity_df)
```



```{r}
# Perform ANOVA
anova_result <- aov(Shannon ~ Project, data = shannon_diversity_df)
tukey_result <- TukeyHSD(anova_result)
library(multcompView)

# Display results
summary(anova_result)
tukey_result
letters <- multcompLetters(tukey_result$Project[, "p adj"])

```

```{r}
# Perform ANOVA (assuming your data is in 'shannon_diversity_df')
anova_result <- aov(Shannon ~ Project, data = shannon_diversity_df)

# Perform Tukey's HSD test for pairwise comparisons
tukey_result <- TukeyHSD(anova_result)

# Extract the p-values from the TukeyHSD result
tukey_pvalues <- tukey_result$Project[, "p adj"]

# Assign names to the comparisons
names(tukey_pvalues) <- rownames(tukey_result$Project)

# Use multcompLetters to get letters for plotting
letters <- multcompLetters(tukey_pvalues)

# Display the letters assigned to each comparison
print(letters)

# Add the letters as a new column to the original data
shannon_diversity_df$Group_Letter <- letters$Letters[match(shannon_diversity_df$Project, names(letters$Letters))]

# View the updated data with group labels
head(shannon_diversity_df)

```






```{r, fig.width=10,fig.height=6}

# Just time series here
# Static version 3-- using transformed abundance, no NAs
# Top IDENTIFIED Phylum
# Aggregate in chron order
  # NOTE: this drops NAs

dat.aglo = tax_glom(ps, taxrank = "Phylum")
dat.trans = transform_sample_counts(dat.aglo, function(x) x/sum(x))
dat.dataframe = psmelt(dat.trans)
dat.agr <- aggregate(Abundance ~ Description2 + Project + Phylum, data = dat.dataframe, FUN = mean, na.action = na.pass)
dat.agr$new_datetime_column <- as.POSIXct(dat.agr$Description2, format = "%m_%d_%y")
dat.agr <- dat.agr[order(dat.agr$new_datetime_column), ]
dat.agr$Description2 <- factor(dat.agr$Description2, levels = unique(dat.agr$Description2))

dat.top30 <- dat.agr %>% 
  group_by(Phylum) %>% 
  summarise(mean_abundance = mean(Abundance)) %>% 
  top_n(30, mean_abundance) %>% 
  inner_join(dat.agr, by = "Phylum")

p <- ggplot(dat.top30, aes(x = Description2, y = Abundance, fill = Phylum)) +
  facet_grid(~Project, scale = "free", space = "free") +
    geom_bar(stat = "identity", color = "black", width = 0.8) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = scales::percent) +
  labs( x = "")

ggsave("16s_community.png", plot = p, width = 14, height = 6, units = "in", dpi = 300)
p_plotly <- ggplotly(p)
p_plotly
```


```{r, fig.width=6,fig.height=4}

# Beta diversity 

# Prep data
relab_genera <-transform_sample_counts(physeq_GOT, function(x) x/sum(x))
sample_data(relab_genera)$Salinity <- as.numeric(sample_data(relab_genera)$Salinity)
non_empty_rows <- rowSums(otu_table(relab_genera)) != 0 # Keep only non-empty rows
relab_genera <- prune_samples(non_empty_rows, relab_genera)
abrel_bray <- phyloseq::distance(relab_genera, method = "bray", na.rm = FALSE) # Calculate bray curtis distance
ps_bray <- merge_phyloseq(relab_genera, as.matrix(abrel_bray))
abrel_ordbray <- ordinate(ps_bray, "PCoA", "bray")

# Create plot
beta_diversity_plot <- plot_ordination(relab_genera, abrel_ordbray, shape = 'Prazi_status') +
  theme_classic() +
  geom_point(aes(color = Salinity, text = paste("Sample ID:", Description, "<br>",
                                               "Day:", Day, "<br>",
                                               "Project:", Project, "<br>",
                                               "Salinity:", Salinity, "<br>",
                                               "Copper:", Copper)), size = 5) + 
  scale_color_gradient(name = "Salinity", low = "lightblue", high = "navyblue")

# Convert ggplot to plotly
beta_diversity_plotly <- ggplotly(beta_diversity_plot)


beta_diversity_plotly
ggsave("beta_plot_sal_16s.png", plot = beta_diversity_plot, width = 6, height = 6, dpi = 300)

```


```{r, fig.width=6,fig.height=4}

# Beta diversity 
# Prep data
sample_data(relab_genera)$Copper <- as.numeric(sample_data(relab_genera)$Copper)
non_empty_rows <- rowSums(otu_table(relab_genera)) != 0 # Keep only non-empty rows
relab_genera <- prune_samples(non_empty_rows, relab_genera)
abrel_bray <- phyloseq::distance(relab_genera, method = "bray", na.rm = FALSE) # Calculate bray curtis distance
ps_bray <- merge_phyloseq(relab_genera, as.matrix(abrel_bray))
abrel_ordbray <- ordinate(ps_bray, "PCoA", "bray")

# Create plot
beta_diversity_plot <- plot_ordination(relab_genera, abrel_ordbray, shape = 'Prazi_status') +
  theme_classic() +
  geom_point(aes(color = Copper, text = paste("Sample ID:", Description, "<br>",
                                               "Day:", Day, "<br>",
                                               "Project:", Project, "<br>",
                                               "Copper Status:", Copper_status)), size = 5) + 
  scale_color_gradient(name = "Copper", low = "pink", high = "brown")

# Convert ggplot to plotly
beta_diversity_plotly <- ggplotly(beta_diversity_plot)


beta_diversity_plotly
ggsave("beta_plot_copper_16s.png", plot = beta_diversity_plot, width = 6, height = 6, dpi = 300)

```

# Random forest
```{r}
library(randomForest)
library(knitr)

#DCS:
predictors <- (otu_table(physeq_GOT))
dim(predictors)

# Make one column for our outcome/response variable 
response <- as.factor(sample_data(physeq_GOT)$DCS)
# Combine them into 1 data frame
rf.data <- data.frame(response, predictors)
set.seed(2)
dcs.classify <- randomForest(response~., data = rf.data, ntree = 100)
print(dcs.classify)

# Make a data frame with predictor names and their importance
imp <- importance(dcs.classify)
imp <- data.frame(predictors = rownames(imp), imp)

# Order the predictor levels by importance
imp.sort <- arrange(imp, desc(MeanDecreaseGini))
imp.sort$predictors <- factor(imp.sort$predictors, levels = imp.sort$predictors)

# Select the top 10 predictors
imp.top20 <- imp.sort[1:20, ]
imp.top20$predictors <- factor(imp.top20$predictors, levels = rev(imp.top20$predictors))



# ggplot
rf_gini <- ggplot(imp.top20, aes(x = predictors, y = MeanDecreaseGini)) +
  geom_bar(stat = "identity", fill = "darkolivegreen3") +
  coord_flip()
ggsave("rf_16s_dcs.png", plot = rf_gini, width = 6, height = 6, dpi = 300)

# Extract OTU names in the order they appear in the bar chart
otunames <- imp.top20$predictors

# Find the matching OTUs in the tax table and reorder them to match the bar chart
r <- rownames(tax_table(physeq_GOT)) %in% otunames
otu_table_ordered <- tax_table(physeq_GOT)[r, ]
otu_table_ordered <- otu_table_ordered[match(otunames, rownames(otu_table_ordered)), ]

# Display the table in the desired order
kable(otu_table_ordered)
```

```{r}

# Salinity:
predictors <- (otu_table(physeq_GOT))
dim(predictors)

# Make one column for our outcome/response variable 
response <- as.factor(sample_data(physeq_GOT)$Sal_status)
# Combine them into 1 data frame
rf.data <- data.frame(response, predictors)
set.seed(2)
sal.classify <- randomForest(response~., data = rf.data, ntree = 100)
print(sal.classify)

# Make a data frame with predictor names and their importance
imp <- importance(sal.classify)
imp <- data.frame(predictors = rownames(imp), imp)

# Order the predictor levels by importance
imp.sort <- arrange(imp, desc(MeanDecreaseGini))
imp.sort$predictors <- factor(imp.sort$predictors, levels = imp.sort$predictors)

# Select the top 10 predictors
imp.top20 <- imp.sort[1:20, ]
imp.top20$predictors <- factor(imp.top20$predictors, levels = rev(imp.top20$predictors))


# ggplot
rf_gini <- ggplot(imp.top20, aes(x = predictors, y = MeanDecreaseGini)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip()
ggsave("rf_16s_sal.png", plot = rf_gini, width = 6, height = 6, dpi = 300)


# Extract OTU names in the order they appear in the bar chart
otunames <- imp.top20$predictors

# Find the matching OTUs in the tax table and reorder them to match the bar chart
r <- rownames(tax_table(physeq_GOT)) %in% otunames
otu_table_ordered <- tax_table(physeq_GOT)[r, ]
otu_table_ordered <- otu_table_ordered[match(otunames, rownames(otu_table_ordered)), ]

# Display the table in the desired order
kable(otu_table_ordered)
```

```{r}

library(reshape2)
library(ggplot2)


confusion_matrix <- sal.classify$confusion
confusion_df <- as.data.frame(confusion_matrix)
confusion_df <- confusion_df[, -ncol(confusion_df)]
confusion_df$Reference <- rownames(confusion_matrix)
confusion_df_melt <- melt(confusion_df, id.vars = "Reference")


confusion_matrix_plot <- ggplot(data = confusion_df_melt, aes(x = Reference, y = variable, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = value), color = "black", size = 5) +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  labs(title = "Confusion Matrix", x = "Actual", y = "Predicted") +
  theme_minimal()

ggsave("confusion_16s_sal.png", plot = confusion_matrix_plot, width = 4.5, height = 4, dpi = 300)


```

```{r}

library(reshape2)
library(ggplot2)


confusion_matrix <- dcs.classify$confusion
confusion_df <- as.data.frame(confusion_matrix)
confusion_df <- confusion_df[, -ncol(confusion_df)]
confusion_df$Reference <- rownames(confusion_matrix)
confusion_df_melt <- melt(confusion_df, id.vars = "Reference")


confusion_matrix_plot <- ggplot(data = confusion_df_melt, aes(x = Reference, y = variable, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = value), color = "black", size = 5) +
  scale_fill_gradient(low = "orange1", high = "darkorange4") +
  labs(title = "Confusion Matrix", x = "Actual", y = "Predicted") +
  theme_minimal()

ggsave("confusion_16s_dcs.png", plot = confusion_matrix_plot, width = 4.5, height = 4, dpi = 300)
confusion_matrix_plot

```

```{r}
library(ggClusterNet)
physeq_GOT
library(ggClusterNet)


# Build a network using Pearson correlation
result <- corMicro(ps = physeq_GOT,N = 100,r.threshold=0.6,p.threshold=0.05,method = "pearson")
# extract cor matrix
cor = result[[1]]


```
# original plot
```{r}
library(sna)
library(tidyfst)


# Build a network using Pearson correlation
result <- corMicro(ps = physeq_GOT,N = 50,r.threshold=0.6,p.threshold=0.05,method = "pearson")
# extract cor matrix


cor = result[[1]]
ps_net = result[[3]]
otu_table = ps_net %>%
  vegan_otu() %>%
  t() %>%
  as.data.frame()
tax_table = ps_net %>%
  vegan_tax() %>%
  as.data.frame()
netClu = data.frame(ID = row.names(tax_table),group =rep(1,length(row.names(tax_table)))[1:length(row.names(tax_table))] )
netClu$group = as.factor(netClu$group)
library(sna)
result2 = PolygonClusterG (cor = cor,nodeGroup =netClu )

node = result2[[1]]
nodes = nodeadd(plotcord =node,otu_table = otu_table,tax_table = tax_table)
edge = edgeBuild(cor = cor,node = node)
pnet <- ggplot() + 
  geom_segment(aes(x = X1, y = Y1, xend = X2, yend = Y2, color = as.factor(cor)),
               data = edge, size = 0.5) +
  geom_point(aes(X1, X2, fill = Family, size = mean), pch = 21, data = nodes) +
  scale_colour_brewer(palette = "Set1") +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  scale_size_continuous(range = c(10, 3)) +  # Adjust point size for plot
  theme(panel.background = element_blank()) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  theme(legend.background = element_rect(colour = NA)) +
  theme(panel.background = element_rect(fill = "white", colour = NA)) +
  theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank()) +
  guides(size = guide_legend(override.aes = list(size = 8)))  # Increase point size in legend

pnet_plotly <- ggplotly(pnet)
pnet_plotly
```

```


```{r}
library(ggrepel)

cor = result[[1]]
ps_net = result[[3]]
otu_table = ps_net %>%
  vegan_otu() %>%
  t() %>%
  as.data.frame()
tax_table = ps_net %>%
  vegan_tax() %>%
  as.data.frame()
netClu = data.frame(ID = row.names(tax_table),group =rep(1,length(row.names(tax_table)))[1:length(row.names(tax_table))] )
netClu$group = as.factor(netClu$group)
library(sna)
result2 = PolygonRrClusterG(cor = cor, nodeGroup = netClu, zoom = 1, zoom2 = 1, bio = F)


node = result2[[1]]
nodes = nodeadd(plotcord =node,otu_table = otu_table,tax_table = tax_table)
edge = edgeBuild(cor = cor,node = node)
pnet <- ggplot() + geom_segment(aes(x = X1, y = Y1, xend = X2, yend = Y2,color = as.factor(cor)),
                                data = edge, size = 0.5) +
  geom_point(aes(X1, X2,fill = Family,size = mean),pch = 21, data = nodes) +
  scale_colour_brewer(palette = "Set1") +
  scale_x_continuous(breaks = NULL) + scale_y_continuous(breaks = NULL) +
  #labs( title = paste(layout,"network",sep = "_"))+
  geom_text_repel(aes(X1, X2,label=Family),size=3, data = nodes)+
  # discard default grid + titles in ggplot2
  theme(panel.background = element_blank()) +
  theme(legend.position = "none") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  theme(legend.background = element_rect(colour = NA)) +
  theme(panel.background = element_rect(fill = "white",  colour = NA)) +
  theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank())
pnet

```

```{r}

cor = result[[1]]
ps_net = result[[3]]
otu_table = ps_net %>%
  vegan_otu() %>%
  t() %>%
  as.data.frame()
tax_table = ps_net %>%
  vegan_tax() %>%
  as.data.frame()
netClu = data.frame(ID = row.names(tax_table),group =rep(1,length(row.names(tax_table)))[1:length(row.names(tax_table))] )
netClu$group = as.factor(netClu$group)
library(sna)
result2 = model_maptree(cor = cor, method = "cluster_fast_greedy", seed = 12)




node = result2[[1]]
nodes = nodeadd(plotcord =node,otu_table = otu_table,tax_table = tax_table)
edge = edgeBuild(cor = cor,node = node)
pnet <- ggplot() + geom_segment(aes(x = X1, y = Y1, xend = X2, yend = Y2,color = as.factor(cor)),
                                data = edge, size = 0.5) +
  geom_point(aes(X1, X2,fill = Family,size = mean),pch = 21, data = nodes) +
  scale_colour_brewer(palette = "Set1") +
  scale_x_continuous(breaks = NULL) + scale_y_continuous(breaks = NULL) +
  #labs( title = paste(layout,"network",sep = "_"))+
  geom_text_repel(aes(X1, X2,label=Family),size=3, data = nodes)+
  # discard default grid + titles in ggplot2
  theme(panel.background = element_blank()) +
  theme(legend.position = "none") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  theme(legend.background = element_rect(colour = NA)) +
  theme(panel.background = element_rect(fill = "white",  colour = NA)) +
  theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank())
pnet

```

```{r}
pnet <- ggplot() + 
  geom_segment(aes(x = X1, y = Y1, xend = X2, yend = Y2, color = as.factor(cor)),
               data = edge, size = 0.5) +
  geom_point(aes(X1, X2, fill = Family, size = mean), pch = 21, data = nodes) +
  scale_colour_brewer(palette = "Set1") +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  scale_size_continuous(range = c(3, 25)) +  # Adjust point size for plot
  theme(panel.background = element_blank()) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  theme(legend.background = element_rect(colour = NA)) +
  theme(panel.background = element_rect(fill = "white", colour = NA)) +
  theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank()) +
  guides(size = guide_legend(override.aes = list(size = 8)))  # Increase point size in legend

pnet
```

```{r}
os <- physeq_GOT
result = corMicro (ps = ps,N = 100,r.threshold=0.8,p.threshold=0.05,method = "pearson")
#Extract correlation matrix
cor = result[[1]]
# building the node group
netClu = data.frame(ID = row.names(cor),group =rep(1:3,length(row.names(cor)))[1:length(row.names(cor))] )
netClu$group = as.factor(netClu$group)
result2 = ranSNEClusterG (cor=  cor,layout ="circle",nodeGroup = netClu)
node = result2[[1]]

```

```{r}
library(plotly)
# plotly version

# Create your ggplot object
pnet <- ggplot() + 
  geom_segment(aes(x = X1, y = Y1, xend = X2, yend = Y2, color = as.factor(cor)),
               data = edge, size = 0.5) +
  geom_point(aes(X1, X2, fill = Family, size = mean), pch = 21, data = nodes) +
  scale_colour_brewer(palette = "Set1") +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  scale_size(range = c(3, 25), guide = "legend") +  # Adjust point size for plot
  theme(panel.background = element_blank()) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  theme(legend.background = element_rect(colour = NA)) +
  theme(panel.background = element_rect(fill = "white", colour = NA)) +
  theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank())

# Convert ggplot to an interactive plotly graph
pnet_plotly <- ggplotly(pnet)

# Display the interactive plot
pnet_plotly

```

```{r}
library(ggplot2)

# Assuming 'nodes' data frame has a column for node labels
nodes$label <- 1:nrow(nodes)  # Add a column with sequential numbers to label each node

# Create your ggplot object with node labels
pnet <- ggplot() + 
  geom_segment(aes(x = X1, y = Y1, xend = X2, yend = Y2, color = as.factor(cor)),
               data = edge, size = 0.5) +
  geom_point(aes(X1, X2, fill = Family, size = mean), pch = 21, data = nodes) +
  geom_text(aes(X1, X2, label = label), data = nodes, size = 3, vjust = 1.5) +  # Add node numbers
  scale_colour_brewer(palette = "Set1") +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  scale_size(range = c(3, 25), guide = "legend") +  
  theme(panel.background = element_blank()) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  theme(legend.background = element_rect(colour = NA)) +
  theme(panel.background = element_rect(fill = "white", colour = NA)) +
  theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank())

# View the ggplot
print(pnet)

```





```{r}
# Load necessary libraries
library(phyloseq)

# Assuming `physeq` is your phyloseq object
# Extract the OTU table
otu_table_df <- as.data.frame(otu_table(physeq))

# Extract sequences from the OTU table
asv_sequences <- rownames(otu_table_df)
# Extract row names from the tax_table for sequence naming
taxa_names <- rownames(tax_table(physeq))

# Create a FASTA formatted character vector
fasta_output <- c()
for (i in seq_along(taxa_names)) {
  fasta_output <- c(fasta_output, paste0(">", taxa_names[i]), taxa_names[i])  # Using taxa names as sequences
}

```


```{r}
library(tibble)

phyloseq::otu_table(physeq_GOT) %>%
  as.data.frame() %>%
  rownames_to_column("id") %>%
  left_join(phyloseq::tax_table(physeq_GOT) %>%
              as.data.frame() %>%
              rownames_to_column("id")) -> physeq_biom


```



```{r}

physeq <- readRDS('ps_16s_decontam.rds')
physeq

```


```{r}
library(microeco)
library(file2meco)


# from phyloseq to microtable object
microtab <- phyloseq2meco(physeq)
microtab
picrust_res <- microtab$picrust2(threads = 4)

```

```{r}
library(Tax4Fun2)
```

```{r}
# Get the current working directory
database_dir <- getwd()

# Optionally, create a specific folder within the working directory
database_dir <- file.path(database_dir, "Tax4Fun2_database")
dir.create(database_dir, showWarnings = FALSE)  # Create directory if it doesn't exist

```




